Global study of well-being and internet adoption | Online analysis supplement

### 2021-11-25 04-model-inference.Rmd
Easier code for forest plots

```{r}
bayes_R2(fits$fit1[[1]], resp = "val")
# Save to file if not done yet
model_criteria_file <- "output/models-bayes-r2.rds"
if (!file.exists(model_criteria_file)) {
  model_criteria <- fits %>% 
    mutate(Year = map(fit1, ~bayes_R2(.x, resp = "val"))) %>% 
    mutate(`Year & internet` = map(fit2, ~bayes_R2(.x, resp = "val"))) %>% 
    select(-fit1, -fit2)
  write_rds(model_criteria, model_criteria_file)
} else {model_criteria <- read_rds(model_criteria_file)}

@@

@@

forest_text <- forest_data %>% 
  drop_na(r_region) %>% 
  select(-c(country, r_country)) %>% 
  pivot_wider(names_from = region, values_from = r_region) %>% 
  group_by(cause) %>% 
  summarise(
    parameters(cur_data_all()[,-c(1:2)], test = "pd", centrality = "mean")
  ) %>% 
  mutate(region = fct_relevel(Parameter, "Average")) %>% 
  mutate(is_average = FALSE) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~if_else(
        cause=="Selfharm", 
        format(round(., 3), nsmall = 3), 
        format(round(., 2), nsmall = 2)
      )
    )
  )

p_tmp <- drop_na(forest_data, r_region) %>% 
  mutate(is_average = region == "Average") %>% 
  ggplot(aes(r_region, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) if_else(x == "Average", "**Average**", x)
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome", 
    breaks = pretty_breaks(), 
    labels = function(x) percent(x/100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  geom_point(
    data = forest_data %>%
      mutate(is_average = TRUE) %>% 
      # This drops a few countries that didn't match region due to string processing above
      drop_na(region),
    aes(x = r_country), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1.25,
    aes(alpha = is_average)
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.9),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_text(
    data = forest_text, family = Font,
    alpha = 1, size = 2.4, hjust = 1, vjust = -0.2,
    aes(
      x = Inf,
      label = str_glue("{Mean} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("cause", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

@@

@@

```{r}
x <- fits_2c$fit[[1]]
y <- emtrends(x, var = "i1_cw", by = c("age", "sex"))
gather_emmeans_draws(y) %>% mean_qi()

contrasts(x$data$sex)
contrasts(x$data$age)
h <- c(
  `Female_10 to 14` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
  `Female_15 to 19` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
  `Female_20 to 24` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0",
  `Male_10 to 14` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*1 + age2:i1_cw*0 = 0",
  `Male_15 to 19` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*0 + age2:i1_cw*1 = 0",
  `Male_20 to 24` = 
    "i1_cw + sex1:i1_cw*1 + age1:i1_cw*-1 + age2:i1_cw*-1 = 0"
)
tmp_avg <- hypothesis(x, h)
tmp_region <- hypothesis(x, h, scope = "coef", group = "region")
```

>>>>

```{r}
# Save to file if not done yet
model_criteria_file <- "output/models-bayes-r2.rds"
if (!file.exists(model_criteria_file)) {
  model_criteria <- fits %>% 
    mutate(Year = map(fit1, ~bayes_R2(.x, resp = "val"))) %>% 
    mutate(`Year & internet` = map(fit2, ~bayes_R2(.x, resp = "val"))) %>% 
    select(-fit1, -fit2)
  write_rds(model_criteria, model_criteria_file)
} else {model_criteria <- read_rds(model_criteria_file)}

@@

### Sex and age

```{r}
x <- fits$fit1[[1]]
get_variables(x)
contrasts(fits$fit1[[1]]$data$sex)
contrasts(fits$fit1[[1]]$data$age)

x <- emtrends(fits$fit1[[1]], var = "year", by = c("sex", "age"), resp = "val")
parameters(x, centrality = "mean", ci_method = "quantile", test = "pd")
tmp <- fits_2c %>% 
  mutate(
    out = map(
      fit, 
      ~emtrends(.x, var = "i1_cw", by = c("sex"), at = list(age1=0, age2=0))
    )
  )
tmp$out[[1]] %>% summary

get_draws <- function(x) {
  draws_region <- spread_draws(
    x, 
    b_val_year, `b_val_year:sex1`, `b_val_year:age1`, `b_val_year:age2`,
    r_region[region, term] | term
  ) %>% 
    mutate(
      `10 to 14` = val_year + b_val_year +
        `val_year:age1`*1 + `b_val_year:age1`*1 +
        `val_year:age2`*0 + `b_val_year:age2`*0,
      `15 to 19` = val_year + b_val_year +
        `val_year:age1`*0 + `b_val_year:age1`*0 +
        `val_year:age2`*1 + `b_val_year:age2`*1,
      `20 to 24` = val_year + b_val_year +
        `val_year:age1`*-1 + `b_val_year:age1`*-1 +
        `val_year:age2`*-1 + `b_val_year:age2`*-1,
      Female = b_val_year + val_year + 
        `val_year:sex1`*1 + `b_sex1:val_year`*1,
      Male = val_year + b_val_year + 
        `val_year:sex1`*-1 + `b_val_year:sex1`*-1
    ) %>% 
    select(region, `10 to 14`:Male)

  draws_avg <- spread_draws(
    x, 
    b_i1_cw, `b_sex1:i1_cw`, `b_age1:i1_cw`, `b_age2:i1_cw`,
  ) %>% 
    mutate(
      `10 to 14` = b_i1_cw + `b_age1:i1_cw`*1 + `b_age2:i1_cw`*0,
      `15 to 19` = b_i1_cw + `b_age1:i1_cw`*0 + `b_age2:i1_cw`*1,
      `20 to 24` = b_i1_cw + `b_age1:i1_cw`*-1 + `b_age2:i1_cw`*-1,
      Female = b_i1_cw + `b_sex1:i1_cw`*1,
      Male = b_i1_cw + `b_sex1:i1_cw`*-1,
      Age = `20 to 24` - `10 to 14`,
      Sex = Female - Male
    ) %>% 
    select(`10 to 14`:Male) %>% 
    mutate(region = "Average")

  draws <- bind_rows(
    "regions" = draws_region,
    "average" = draws_avg, 
    .id = "Level"
  ) %>% 
    mutate(region = str_replace(region, "\\.", "\n")) %>% 
    ungroup()
  draws
}
```

@@

forest_text <- forest_data %>% 
  drop_na(r_region) %>% 
  select(-c(country, r_country)) %>% 
  pivot_wider(names_from = region, values_from = r_region) %>% 
  group_by(cause) %>% 
  summarise(
    parameters(
      cur_data_all()[,-c(1:2)], 
      test = "pd", 
      centrality = "mean",
      ci_method = "quantile"
    )
  ) %>% 
  mutate(region = fct_relevel(Parameter, "Average")) %>% 
  mutate(is_average = FALSE) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~if_else(
        cause=="Selfharm", 
        format(round(., 3), nsmall = 3), 
        format(round(., 2), nsmall = 2)
      )
    )
  )

p_tmp <- drop_na(forest_data, r_region) %>% 
  mutate(is_average = region == "Average") %>% 
  ggplot(aes(r_region, region, fill = is_average)) +
  scale_fill_manual(values = c("dodgerblue1", "dodgerblue4")) +
  scale_alpha_manual(values = c(.4, .8)) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_shape_manual(values = c(21, 19)) +
  scale_y_discrete(
    expand = expansion(c(0.01, .1)),
    labels = function(x) if_else(x == "Average", "**Average**", x)
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome", 
    breaks = pretty_breaks(), 
    labels = function(x) percent(x/100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.1, .1))
  ) +
  geom_point(
    data = forest_data %>%
      mutate(is_average = TRUE) %>% 
      # This drops a few countries that didn't match region due to string processing above
      drop_na(region),
    aes(x = r_country), size = 1, col = "dodgerblue1",
    position = position_nudge(0, -0.075), alpha = .4
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1,
    aes(alpha = is_average)
  ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = 1,
    point_size = 1.75,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0)),
    position = position_nudge(0, 0)
  ) +
  geom_text(
    data = forest_text, family = Font,
    alpha = 1, size = 2.4, hjust = 1, vjust = -0.2,
    aes(
      x = Inf,
      label = str_glue("{Mean} [{CI_low}, {CI_high}]")
    )
  ) +
  facet_wrap("cause", nrow = 1, scales = "free_x") +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_markdown(),
    legend.position = "none"
  )

@@

A table of smallest and greatest country-level estimates

```{r}
forest_data %>% 
  drop_na(country) %>% 
  select(-.draw, -r_region) %>% 
  group_by(cause) %>% 
  filter(
    r_country %in% 
      c(min(r_country, na.rm = T), max(r_country, na.rm = T))
  ) %>% 
  kbl() %>% 
  kable_paper(html_font = Font, full_width = FALSE)
```

@@

```{r}
get_coefs <- function(x) {
  h <- c(
    `10 to 14` = 
      "i1_cw + age1:i1_cw*1 + age2:i1_cw*0 = 0",
    `15 to 19` = 
      "i1_cw + age1:i1_cw*0 + age2:i1_cw*1 = 0",
    `20 to 24` = 
      "i1_cw + age1:i1_cw*-1 + age2:i1_cw*-1 = 0",
    `Female` = 
      "i1_cw + sex1:i1_cw*1 = 0",
    `Male` = 
      "i1_cw + sex1:i1_cw*-1 = 0"
  )

  # Average samples
  avg_h <- hypothesis(x, h)
  avg_s <- avg_h$samples %>% as_tibble()
  names(avg_s) <- avg_h$hypothesis$Hypothesis  
  avg_s <- avg_s %>% 
    pivot_longer(everything()) %>% 
    mutate(name = paste("Average", name, sep = "-"))

  # Region samples
  region_h <- hypothesis(x, h, scope = "coef", group = "region")
  region_s <- region_h$samples %>% as_tibble()
  names(region_s) <- paste(
    region_h$hypothesis$Group, 
    region_h$hypothesis$Hypothesis, 
    sep = "-"
  )
  region_s <- region_s %>% 
    pivot_longer(everything())

  # Country means
  country_h <- hypothesis(
    x, h, scope = "ranef", group = "country"
  )$hypothesis %>% 
    as_tibble()
  country_h <- country_h %>% 
    left_join(
      distinct(x$data, region, country), 
      by = c("Group" = "country")
    ) %>% 
    select(region, Hypothesis, Estimate, country = Group)

  # Add region coefs to country ranefs
  country_h <- left_join(
    country_h, 
    region_h$hypothesis %>% 
      rename(region = Group, coef = Estimate)
  ) %>% 
    mutate(Estimate = Estimate + coef)

  # Join all to one data frame
  samples <- bind_rows(avg_s, region_s) %>% 
    separate(name, into = c("region", "Hypothesis"), sep = "-") %>% 
    bind_rows(country_h)

  # Verify that naming worked
  # region_h$hypothesis %>% 
  #   left_join(
  #     samples %>% 
  #       group_by(region, Hypothesis) %>% 
  #       summarise(xxx = mean(value)),
  #     by = c("Group" = "region", "Hypothesis")
  #   ) %>% 
  #   as_tibble() %>% 
  #   filter(xxx != Estimate)

  samples
}
tmp <- fits %>% 
  mutate(out = map(fit2, get_coefs)) %>% 
  select(-fit1, -fit2)

tmp <- tmp %>% 
  unnest(out) %>% 
  mutate(is_average = region=="Average") %>% 
  mutate(region = fct_relevel(region, "Average")) %>% 
  mutate(panel = if_else(str_detect(Hypothesis, "ale"), "Sex", "Age")) %>% 
  mutate(
    side = if_else(Hypothesis %in% c("10 to 14", "Female"), "top", "bottom")
  )

tmp_regions <- tmp %>% 
  filter(is.na(country)) %>% 
  filter(Hypothesis != "15 to 19")

tmp_countries <- tmp %>% 
  filter(!is.na(country)) %>% 
  filter(Hypothesis != "15 to 19") %>% 
  mutate(is_average = FALSE)

tmp_text <- tmp_regions %>% 
  select(cause, region, Hypothesis, value) %>% 
  group_by(cause, region, Hypothesis) %>% 
  mutate(.draw = 1:n()) %>% 
  pivot_wider(names_from = Hypothesis, values_from = value) %>%
  mutate(Age = `20 to 24` - `10 to 14`, Sex = Female - Male) %>% 
  summarise(
    parameters(
      cur_data_all() %>% select(Age, Sex), 
      test = "pd", 
      centrality = "mean",
      ci_method = "quantile"
    )
  ) %>% 
  mutate(
    across(
      where(is.numeric), 
      ~if_else(
        cause=="Selfharm", 
        format(round(., 3), nsmall = 3), 
        format(round(., 2), nsmall = 2)
      )
    )
  ) %>% 
  mutate(is_average = region=="Average") %>% 
  mutate(region = fct_relevel(region, "Average")) %>% 
  mutate(panel = Parameter)

tmp_regions %>%   
  ggplot(aes(value, region, col = Hypothesis, fill = Hypothesis)) +
  scale_alpha_manual(values = c(.3, .6)) +
  scale_color_brewer(
    "Group",
    palette = "Set1",
    aesthetics = c("color", "fill")
  ) +
  scale_shape_manual(
    values = c(21, 19), guide = "none"
  ) +
  geom_vline(xintercept = 0, lty = 2, size = .2) +
  scale_y_discrete(
    expand = expansion(c(0.1, .1)),
    labels = function(x) if_else(x == "Average", "**Average**", x)
  ) +
  scale_x_continuous(
    "Conditional effect of 100% increase in internet adoption on outcome", 
    breaks = pretty_breaks(), 
    labels = function(x) percent(x/100, .01) %>% str_remove("\\.00"),
    expand = expansion(c(.01, .1))
  ) +
  stat_halfeye(
    point_interval = NULL, normalize = "panels", 
    height = .75, adjust = 1,
    aes(side = side, group = side, alpha = is_average), 
    show.legend = FALSE
  ) +
  # geom_point(
  #   data = tmp_countries %>% 
  #     drop_na(region),
  #   aes(x = Estimate, shape = Star=="*"),
  #   size = .5, alpha = .4, fill = "white",
  #   position = position_dodge2v(.5)
  # ) +
  stat_pointinterval(
    alpha = 1, .width = c(.95),
    interval_size = .4,
    point_size = 1.5,
    fill = "white",
    aes(shape = after_stat(xmin > 0 | xmax < 0), group = side),
    position = position_dodgev(.2), key_glyph = draw_key_point
  ) +
  geom_richtext(
    data = tmp_text %>% 
      mutate(Hypothesis = NA) %>% 
      mutate(
        Mean = if_else(
          as.numeric(pd) >= .95,
          str_glue("**{Mean}**"), 
          Mean
        ),
      ),
    aes(
      x = Inf,
      label = str_glue("{Mean} [{CI_low}, {CI_high}]")
    ),
    size = 2.5, hjust = 1, col = "black", 
    family = Font, label.color = NA, 
    label.padding = unit(0, "pt"),
    show.legend = FALSE
  ) +
  facet_grid2(panel ~ cause, scales = "free_x", axes = "x") +
  theme(
    legend.position = "right",
    axis.title.y = element_blank(),
    axis.text.y = element_markdown()
  )
```
